
\resumesection{Professional Experience}

\normalsize
\resumesubsection{Los Alamos National Laboratory}{Los Alamos, New Mexico}

\begin{minipage}{\textwidth}
   %\begin{center}
     \begin{tabular}{r|ll}
	     2016 - \emph{Present} & \textbf{Graduate Research Assistant}  & \textit{NEN-5, Systems Design \& Analysis} \\
	     2016 - \emph{Present} & \textbf{Graduate Research Assistant} & \textit{ISR-1, Space Science \& Applications} \\
	     2011 - 2012 & \textbf{Post Master's Research Assistant}  & \textit{W-13, Advanced Engineering Analysis} \\
	     2010 & \textbf{Summer Intern} & \textit{XCP-3, Monte Carlo Codes} \\
     \end{tabular}
   %\end{center}
\end{minipage}

\begin{center}
	\begin{minipage}{\textwidth}
	\begin{itemize}
	   %\item Gained significant experience in the development
	    %\item Utilized SQL databases for
	    \item Implemented new features in \textsc{MCNP6} through writing code, developing benchmarks, publishing reports, and presenting the features at various conferences [Pubs: \ref{ieee_nss_paper},\ref{ans_summer2017_paper},\ref{ans_summer2017_jrt_paper},\ref{caari_2016_paper_1},\ref{caari_2016_paper_2},\ref{ans_winter2016_paper}].
	    \item Gained significant knowledge and experience in the design, modeling, simulation, and analysis of a variety of radiation detectors for the Nuclear Detection Figure of Merit (NDFOM) project.
	    \item Transitioned NDFOM from version 2.0 to 3.0 by modularizing and refactoring the backend Python code and through developing a cleaner, more intuitive user interface for the customer.
	    %\item Managed the deployed server of NDFOM, including SQL database
            %\item Utilized SQL databases, managing servers, and utilizing version control using Mercurial
	    \item Assisted in the development, testing, validation, and verification of the combined radiation transport and finite-element analysis multi-physics capability for the Engineering Campaign-7 Nuclear Survivability project [Pubs: \ref{useful_prompt},\ref{mcnp_efforts}].
	    \item Developed unstructured mesh human phantoms for health physics applications with \textsc{MCNP6} [Pubs: \ref{ans_2012_paper},\ref{abaqus_2012_paper}].
	    %\item \textsuperscript{*}Acquired DOE Q-level security clearance and Sigmas 1-10,11,12,13,15 and performed analysis on the W-88 system
	    \item \textsuperscript{*}Acquired DOE Q-level security clearance and assisted on the analysis of weapons systems.
	    \item Created a software visualization package for finite element geometries in MCNP simulations.
	    \item Utilized high performance computing (HPC) systems and utilities for advanced physics simulations and analysis.
	    %\item Programs: \textsc{MCNP}, Django, HTML, Javascript, SQL, Mercurial, Version Control, Python\textsuperscript{1,2,3,4}
	    %\item Modeling detector system responses using \textsc{MCNP}, Django, HTML, Javascript, and Python
            %\item Utilized SQL databases, managing servers, and utilizing version control using Mercurial
	    %\item Programs: \textsc{MCNP}, Django, HTML, Javascript, SQL, Mercurial, Version Control, Python
	    %\item Modeling detector system responses using \textsc{MCNP}, Django, HTML, Javascript, and Python
	    %\item Developed benchmarks and publishing reports on newly implemented features in MCNP [Pubs: \ref{ans_summer2017_paper},\ref{caari_2016_paper_1},\ref{caari_2016_paper_2},\ref{ans_winter2016_paper}] 
	    %\item Performed group collaboration on a variety of software projects 
	    %\item Campaign-7 testing, validation, and verification of the multi-physics coupling of the W-88 system
	\end{itemize}
\end{minipage}
    \end{center}

\begin{minipage}{\textwidth}
\begin{center}
\footnotesize \textsuperscript{*} Paperwork submitted June, 2016 for reinstatement of DOE Q-level clearance.
\end{center}
\end{minipage}

\resumesubsection{Medical College of Wisconsin}{Milwaukee, Wisconsin}

\begin{minipage}{\textwidth}
	\begin{tabular}{r|ll}
		2012 - 2016 & \textbf{Graduate Research Assistant} & \textit{Department of Biophysics}  \\
		2014 - 2016 & \textbf{Biophysics Representative, IT Liaison} & \textit{Graduate Student Council}  \\
			%\textbf{Information Technology Liason} & \textit{Graduate School of Biomedical Sciences} & 2015-2016 \\
	\end{tabular}
\end{minipage}

\begin{minipage}{\textwidth}
	\begin{itemize}
	%\item Conducted background research and provided the preliminary results necessary to secure funding through a co-authored \href{https://grants.nih.gov/grants/funding/r21.htm}{\textbf{R21}} National Institutes of Health (NIH) grant
	\item Conducted background research, provided preliminary results, and assisted in the writing of an R21 National Institute of Health (NIH) research grant to help fund my graduate research.
	%\item Secured funding for my graduate studies by conducting the background research, providing the preliminary results, and co-authoring a successful \href{https://grants.nih.gov/grants/funding/r21.htm}{\textbf{R21}} National Institute of Health (NIH) grant
   	\item Patented a segmented reconstruction technique for artifact reduction in Magnetic Resonance Imaging [Pat: \ref{lqsm_patent}].
	\item Collaborated with a diverse group of professionals, including medical doctors and imaging technologists, to perform clinical research, meet deliverables, and submit the findings to various international conferences [Pubs: \ref{ismrm_2016_paper},\ref{cmrr_2015_paper},\ref{ismrm_2014_paper}].
	%\item Performed research full cycle, from 
	\item Gained hands-on technical and experimental research skills by working in a laboratory and acquiring data while performing research on animals.
	%\item Performed full cycle research from the background, planning
	%\item Collected my own data, provided the necessary care for our experimental animals, and expanded my laboratory and engineering skills by performing a variety of hands-on experimental and engineering tasks
	\item Facilitated communication between students, staff, and the university's Information Technology (IT) team as the graduate school IT liaison.
	%\item Collected pre-clinical experimental data on imaging animals
	%\item Expanded experimental capabilities by my own data, caring for animals, and performing hands-on experiments
	%\item Interacted directly with clinical patients and subjects to collect patient data for clinical studies
	%\item Facilitated communication between students and staff in the graduate school with the university's Information Technology group
	%\item Communicated the concerns of the entire graduate student body with the university's Information Technology team
	%\item Provided technical leadership and guidance on Information Technology (IT) needs to all MCW Graduate students as the system Liason
	%\item Demonstrated an ability to interact with patients in a clinical setting in addition to handling animals for pre-clinical translation 
	%\item Served as the point-of-contact the Biophysics department and the Graduate School at MCW
	%\item Served as the graduate school Information Technology (IT) liason
	%\item Represented the Biophysics department i
	%\item Served as the Representative for the
	%\item Served on the Graduate Student Council as Biophysics representative and Information Technology liaison
	%\item Collaborated with faculty, staff, and medical students to address and improve graduate school IT needs
	\end{itemize}
\end{minipage}

\resumesubsection{University of Wisconsin - Madison}{Madison, Wisconsin}

\begin{minipage}{\textwidth}
		\begin{tabular}{rll}
			2008 - 2011 & \textbf{Student Research Assistant} & \textit{Department of Medical Physics} \\
			2010 - 2011 & \textbf{Chapter President} & \textit{American Nuclear Society (ANS)} \\
		\end{tabular}
\end{minipage}

\begin{minipage}{\textwidth}
	\begin{itemize}
		%\item Assisted in research, modeling, and analysis of brachytherapy seed quality assurance methods
		\item Researched methods for non-invasive quality assurance assessment of radioactive brachytherapy seeds.
		%\item Assisted in research, modeling, and analysis of brachytherapy seed quality assurance methods
		\item Managed the American Nuclear Society organizational duties, including activities such as recruiting guest speakers to present at meetings, organizing conference travel, and arranging public outreach events.
		\item Mentored and taught a variety of students through volunteering at various events, such as Science Olympiad, middle and high school science fairs, and local Boy Scout chapters on achieving their Nuclear Science Merit Badge.
		%\item \textit{WE CAN STILL ADD ONE MORE HOPEFULLY, so BE SURE TO DO IT!!!}
	\end{itemize}
\end{minipage}
